\begin{thebibliography}{99}% more than 9 --> 99 / less than 10 --> 9

\bibitem{K8s2017}
The Kubernetes Authors, Kubernetes | Production-Grade Container Orchestration, https://kubernetes.io/, accessed July 14, 2017

\bibitem{K8sFederation2017}
The Kubernetes Authors, Federation, \url{https://kubernetes.io/docs/concepts/cluster-administration/federation/}, accessed July 14, 2017

\bibitem{K8sIngress2017}
The Kubernetes Authors, Ingress Resources | Kubernetes, \url{https://kubernetes.io/docs/concepts/services-networking/ingress/}, accessed July 14, 2017

\bibitem{Zhang2000}
Zhang W., Linux virtual server for scalable network services, Ottawa Linux Symposium, 2000

\bibitem{Pleshakov2016}
Michael Pleshakov, NGINX and NGINX Plus Ingress Controllers for Kubernetes Load Balancing, \url{https://www.nginx.com/blog/nginx-plus-ingress-controller-kubernetes-load-balancing/}, accessed July 14, 2017

\bibitem{NginxInc2016}
NGINX Inc., NGINX Ingress Controller, \url{https://github.com/nginxinc/kubernetes-ingress}, accessed July 14, 2017

\bibitem{Prashanth2016}
Prashanth B, Mike Danese, Bowei Du, kube-keepalived-vip, \url{https://github.com/kubernetes/contrib/tree/master/keepalived-vip}, accessed July 14, 2017

\bibitem{ACassen2016}
Alexandre Cassen, Keepalived for Linux, \url{http://www.keepalived.org/}, accessed July 14, 2017

\bibitem{Sibiryov2015}
Andrey Sibiryov, GORB Go Routing and Balancing, \url{https://github.com/kobolog/gorb}, accessed July 14, 2017

\bibitem{Aaltodoc:http://urn.fi/URN:NBN:fi:aalto-201611025433}
Marttila Tero, Design and Implementation of the clusterf Load Balancer for Docker Clusters, Master's Thesis, Aalto University, October, 2016

\bibitem{DockerCoreEngineering2016}
Docker Core Engineering, Docker 1.12: Now with Built-in Orchestration, \url{https://blog.docker.com/2016/06/docker-1-12-built-in-orchestration/}, accessed July 14, 2017

\bibitem{DockerInc2017}
Docker Inc, Use swarm mode routing mesh | Docker Documentation, \url{https://docs.docker.com/engine/swarm/ingress/}, accessed July 14, 2017

\bibitem{MartinA.Brown2017}
Martin A. Brown, Guide to IP Layer Network Administration with Linux, \url{http://linux-ip.net/html/index.html}, accessed July 14, 2017

\bibitem{CoreOSEtcd}
CoreOS Inc, etcd | etcd Cluster by CoreOS, \url{https://coreos.com/etcd}, accessed July 14, 2017 

\bibitem{HashiCorpConsul}
HashiCorp, Consul by HashiCorp, \url{https://www.consul.io/}, accessed July 14, 2017

\bibitem{ktaka_ccmp_2017_826894}
K. Takahashi, ktaka-ccmp/ipvs-ingress, \url{https://doi.org/10.5281/zenodo.826894}, July, 2017

\bibitem{Glozer2016}
Will Glozer, wrk - a HTTP benchmarking tool, \url{https://github.com/wg/wrk}, accessed July 14, 2017

\bibitem{Marmol2015}
Marmol, V., Jnagal, R., and Hockin, T. (2015). Networking in containers and container clusters. Proceedings of netdev 0.1, February.

\bibitem{hinden2004virtual}
Hinden, R. (2004). Virtual router redundancy protocol (VRRP) (No. RFC 3768).

\bibitem{moy1997ospf}
Moy, J. (1997). OSPF version 2 (No. RFC 2178).

\bibitem{eisenbud2016maglev}
Eisenbud, D. E., Yi, C., Contavalli, C., Smith, C., Kononov, R., Mann-Hielscher, E., ... and Hosein, J. D. (2016, March). Maglev: A Fast and Reliable Software Network Load Balancer. In NSDI (pp. 523-535).

\bibitem{patel2013ananta}
Patel, P., Bansal, D., Yuan, L., Murthy, A., Greenberg, A., Maltz, D. A., ... and Kim, C. (2013). Ananta: Cloud scale load balancing. ACM SIGCOMM Computer Communication Review, 43(4), 207-218.

\bibitem{takahashi2018portable}
Takahashi, K., Aida, K., Tanjo, T., and Sun, J. (2018, January). A Portable Load Balancer for Kubernetes Cluster. In Proceedings of the International Conference on High Performance Computing in Asia-Pacific Region (pp. 222-231). ACM.

\bibitem{project_calico}
Project Calico, Secure Networking for the Cloud Native Era, \url{https://www.projectcalico.org/}, 2018, accessed August 14, 2018

\bibitem{coreos_2018}
Coreos Inc., coreos/flannel, \url{https://github.com/coreos/flannel}, accessed August 14, 2018

\bibitem{exa-networks_2018}
Exa-Networks, Exa-Networks/exabgp, \url{https://github.com/Exa-Networks/exabgp}, accessed August 14, 2018

\bibitem{osrg_gobgp_zebra}
Osrg, osrg/gobgp, \url{https://github.com/osrg/gobgp/blob/master/docs/sources/zebra.md}, accessed August 14, 2018

\bibitem{ip-sysctl}
ip-sysctl.txt, \url{https://www.kernel.org/doc/Documentation/networking/ip-sysctl.txt}, accessed August 14, 2018

\bibitem{rfc7911}
Walton, D., Retana, A., Chen, E., and Scudder, J. (2016). Advertisement of multiple paths in BGP (No. RFC 7911).

\bibitem{rfc4456}
Bates, T., Chen, E., and  Chandra, R. (2006). Bgp route reflection: An alternative to full mesh internal bgp (ibgp) (No. RFC 4456).

\bibitem{thaler2000multipath}
Thaler, D., and Hopps, C. (2000). Multipath issues in unicast and multicast next-hop selection (No. RFC 2991).

\end{thebibliography}
