
\profile*{Kimitoshi Takahashi}{received the B.S. degree from Tokyo University in 1993.
During 1993--2002, he stayed at Fujitsu Labs. Limited and worked in the field of semiconductor lithography. 
Form 1999 to 2000 he stayed at Stanford University as a visiting scholar.
In 2002, he founded Cluster Computing Inc. and stayed as CEO since then. 
Since 2016, he has also been Ph.D candidate at the Graduate University for Advanced Studies.}%

\profile*{Kento Aida}{received Dr. Eng. in electrical engineering from Waseda University in 1997. He became a research associate at Waseda University in 1992. He joined Tokyo Institute of Technology and became a research scientist at the Department of Mathematical and Computing Sciences in 1997, an assistant professor at the Department of Computational Intelligence and Systems Science in 1999, and an associate professor at the Department of Information Processing in 2003, respectively. He is now a professor at National Institute of Informatics from 2007. He was also a researcher at PRESTO in Japan Science and Technology Agency (JST) from 2001 through 2005, a research scholar at the Information and Computer Sciences Department in University of Hawai`i in 2007, and a visiting professor at the Department of Information Processing in Tokyo Institute of Technology from 2007 through 2016.}

\profile*{Tomoya Tanjo}{}

\profile*{Jingtao Sun}
{received his M.E degrees in computer science from Tokyo University of Technology, Japan in 2013, and received his Ph.D degrees in informatics from the Graduate University for Advanced Studies, Japan in 2016. Since 2016, he joined National Institute of Informatics and became a project researcher at the Information Systems Architecture Research Division. During 2016–2018, he visited Florida University and University of Maryland, Baltimore County as a visiting researcher. His current research insterests include distributed systems, cloud computing, and Internt of Things. He is a member of JPSJ, CCF, IEEE and ACM.}

\profile*{Kazushige Saga}{}
